Structured Versus Decorated Cospans

### 2020-12-07 cospans.tex
Changed statement of Lem. 3.4, statement and proof of Lem. 3.6

\begin{lem}[\textbf{Gray}] \label{prop:opfibtolari}
  Let $U \maps\X \to \A$ be an opfibration. Then $U$ is a rali if (and only if) fibers are equipped with initial objects that are preserved up to isomorphism by the reindexing functors.
\end{lem}

\begin{proof}
 This is \cite[Proposition~4.4]{Gray}; we only need the ``if'' direction here.    Suppose each fiber $\X_a$ of the opfibration $U$ is equipped with an initial object $\bot_a$, and these objects are preserved by the reindexing functors.   Define $L\maps\A\to\X$ on objects $a \in \A$ by $L(a) = \bot_a$.   Define $L$ on morphisms as follows: given $f\maps a\to a'$, $L(f)$ is the composite
 \begin{equation}\label{eq:Lonarrows}
  \bot_a\xrightarrow{\mathrm{Cocart}(f,\bot_a)}f_!(\bot_a)\stackrel{\chi_a}{\cong}\bot_{a'}
 \end{equation}
where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$  and $\chi_a$ is the unique isomorphism between the initial objects in the fiber above $a'$, since $f_!$ preserves them.   One can make $U$ into a right adjoint of $L$ with unit $a \mapsto U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.
\end{proof}

>>>>

\begin{lem}[\textbf{Gray}] \label{prop:opfibtolari}
Let $U \maps\X \to \A$ be an opfibration. Then to make $U$ into a rali, it suffices to equip
its fibers with initial objects that are preserved up to isomorphism by the reindexing functors.
\end{lem}

\begin{proof}
 This is \cite[Proposition~4.4]{Gray}.    Suppose each fiber $\X_a$ of the opfibration $U$ is equipped with an initial object $\bot_a$, and these objects are preserved by the reindexing functors.   Define $L\maps\A\to\X$ on objects $a \in \A$ by $L(a) = \bot_a$.   Define $L$ on morphisms as follows: given $f\maps a\to a'$, $L(f)$ is the composite
 \begin{equation}\label{eq:Lonarrows}
  \bot_a\xrightarrow{\mathrm{Cocart}(f,\bot_a)}f_!(\bot_a)\stackrel{\chi_a}{\cong}\bot_{a'}
 \end{equation}
where $\mathrm{Cocart}(f,\bot_a)$ is the cocartesian lifting of $f$ to $\bot_a$  and $\chi_a$ is the unique isomorphism between the initial objects in the fiber above $a'$, since $f_!$ preserves them.   One can then make $U$ into a right adjoint of $L$ with unit $\iota_a \maps a \to U(L(a))$ being the identity, using the fact that $U(L(a)) = U(\bot_a) = a$.
\end{proof}
